Multiparty Session Type-safe Web Development in TypeScript

### 2020-01-21 PLACES_2020/paper.tex
PLACES 2020: progress on front-end API encoding

\paragraph{Components} A component is a reusable UI element which contains its own markup and logic. Components implement a \texttt{render()} function which returns a React element, the smallest building blocks of a React application. Components can keep \textit{state} and the \texttt{render()} function is invoked upon a change of state. A simple counter can be implemented as a component, with the count stored as state, a button which increments the count when clicked and a \texttt{div} that renders the current count. Components can also render other components, which gives rise

@@

\paragraph{Uni-directional data flow} Parent components pass data to child components as \textit{props}, \dots

% Parent provides props to child (uni-directional workflow)

@@

@@

\paragraph{Repeat use} \dots

>>>>

\paragraph{Components} A component is a reusable UI element which contains its own markup and logic. Components implement a \texttt{render()} function which returns a React element, the smallest building blocks of a React application. Components can keep \textit{state} and the \texttt{render()} function is invoked upon a change of state. A simple counter can be implemented as a component, with the count stored as state, a button which increments the count when clicked and a \texttt{div} that renders the current count. Components can also render other components, which gives rise to a parent/child relationship between components. Parents can pass data to children as \textit{props}, so the counter component could render a  child component \texttt{<StyledDiv count=\{this.state.count\} />} and propagate the count in the state to the child to reuse an existing UI element.

@@

@@

\paragraph{State} \dots

\paragraph{Model transitions - message receive} \dots

\paragraph{Model transitions - message send} \dots

\subsubsection{Session instantiation}

\dots

@@

\paragraph{Repeat use} Communication channels are not exposed to the programmer so multiple sends are impossible. This does not restrict the programmer from binding the send action to exactly one UI event: for the \textit{Noughts and Crosses} game, we bind the \texttt{Pos(Point)} send action to each unoccupied cell on the game board, but the generated runtime ensures that, once an event bound to the send action is triggered, the send is only performed once and the successor state is rendered on the DOM to prevent multiple sends initiated by the user.
